Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-08-25 R0V0.tex
changed the gitignore
Change notation of ordered sets.

\author{Humberto~Stein Shiromoto,~\IEEEmembership{Member,~IEEE,}
        Ian~R. Manchester,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\thanks{Both authors are with the Department of Aerospace, Mechanical, and Mechatronic Engineering and The Australian Centre for Field Robotics. Address: The
Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: humberto.shiromoto@ieee.org. ORCID: 0000-0002-0883-0231, }% <-this % stops a space
}

@@

\paragraph{Notation.} Let $N\in\mathbb{N}$ be a constant value. The notation $\mathbb{N}_{[1,N]}$ stands for the set $\{i\in\mathbb{N}:1\leq i\leq N\}$. Let $c\in\mathbb{R}$ be a constant value. The notation $\mathbb{R}_{[1,c]}$ (resp. $\mathbb{R}_{\diamond c}$) stands for the set $\{x\in\mathbb{R}:1\leq x\leq c\}$ (resp.  $\{x\in\mathbb{R}:x\diamond c\}$, where $\diamond$ is a comparison operator, i.e., $\diamond\in\{<,\geq,=,\ \text{etc}\}$). A matrix $M\in\mathbb{R}^{n\times n}$ with zero elements except (possibly) those  $m_{ii},\ldots,m_{nn}$ on the diagonal is denoted as $\mathbin{\mathtt{diag}}(m_{ii},\ldots,m_{nn})$. The notation $M\succ 0$ (resp. $M\succeq 0$) stands for $M$ being positive (resp. semi)definite.

>>>>

\author{Humberto~Stein Shiromoto,~\IEEEmembership{Member,~IEEE,}
        Ian~R. Manchester,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\thanks{Both authors are with the Department of Aerospace, Mechanical, and Mechatronic Engineering and The Australian Centre for Field Robotics. Address: The
Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: {\tt humberto.shiromoto@ieee.org}, {\tt orcid.org/0000-0002-0883-0231}}% <-this % stops a space
}

@@

\paragraph{Notation.} Let $\mathbb{S}$ be a totally ordered set and $s_1,s_2,s_3\in\mathbb{S}$. The notation $\mathbb{S}_{[s_1,s_2)}$ (resp. $\mathbb{S}_{\diamond s_3}$) stands for the set $\{s\in\mathbb{S}:s_1\leq s< s_2\}$ (resp. $\{s\in\mathbb{S}:s\diamond s_3\}$, where $\diamond$ is a comparison operator, i.e., $\diamond\in\{<,\geq,=,\ \text{etc}\}$). A matrix $M\in\mathbb{R}^{n\times n}$ with zero elements except (possibly) those  $m_{ii},\ldots,m_{nn}$ on the diagonal is denoted as $\mathbin{\mathtt{diag}}(m_{ii},\ldots,m_{nn})$. The notation $M\succ 0$ (resp. $M\succeq 0$) stands for $M$ being positive (resp. semi)definite.
